Viscous Transport in Eroding Porous Media

### 2019-06-19 docs/transport/erosion_transport.tex
add new figs in transport paper
do the result section in transport paper

In~\cite{qua-moo2018}, we observed that erosion causes the space
between nearly touching bodies to quickly expand, and flat faces develop
along the region of near contact.  This qualitative behavior is also
observed In Figure~\ref{fig:Eroding20vort}, such as between bodies 3
\&4 and 15 \& 16.  However, by resolving bodies that are
much closer to one another when compared to our previous
work~\cite{qua-moo2018}, we see that it is possible for very little
erosion to occur between a pair of bodies.  In particular, for pairs of
bodies where the channel between the bodies is nearly perpendicular to
the main flow direction (bodies 1 \& 6, 3 \& 9, and 13 \& 15), there is
very little shear stress and the effect of erosion is slight.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256$.}
\end{center}
\end{figure}

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
In Fig.~\ref{fig:Eroding100vort}

@@

In Fig.~\ref{fig:Eroding100tort}(b) we record the 
local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is
is 1.2547 and the minimum is 1.0003. This function $\tau$
has more jumps than the one in the case of 20 bodies but its maximum 
is smaller than the maximum in the case of 20 bodies. 
The jump in this graph means the neighboring trajectories are splitted by bodies
so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
since there are more bodies in the former case. To understand the meaning of jump 
of $\tau$, we use the data we got from local tortuosity $\tau(y)$
to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
then rejoin with each other and it causes the difference of $\tau$ with respect to the neighboring trajectories.   
We also can get the idea why the maximum value of $\tau$ is smaller 
than the one in the case of 20 bodies . 
The most of the bodies in this case are smaller than those in the case of 20 bodies.
So when two neighboring trajectories are splitted on the left side by a smaller body they do not
travel as far as the two splitted by a bigger body do after they rejoin on the right side.

}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The historical trajectories of 
200 tracers released at x = -1 in the fluid with multiple bodies.}
\end{center}
\end{figure}

>>>>

In~\cite{qua-moo2018}, we observed that erosion causes the space
between nearly touching bodies to quickly expand, and flat faces develop
along the region of near contact.  This qualitative behavior is also
observed in Figure~\ref{fig:Eroding20vort}, such as between bodies 3
\&4 and 15 \& 16.  However, by resolving bodies that are
much closer to one another when compared to our previous
work~\cite{qua-moo2018}, we see that it is possible for very little
erosion to occur between a pair of bodies.  In particular, for pairs of
bodies where the channel between the bodies is nearly perpendicular to
the main flow direction (bodies 1 \& 6, 3 \& 9, and 5 \& 13), there is
very little shear stress and the effect of erosion is slight.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{100 bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[H]
 \begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_50}
\caption{100 bodies at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_100}
\caption{99 bodies at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =0.9\linewidth]{./figs/100b_150}
\caption{94 bodies at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =1.1\linewidth]{./figs/100b_200}
\caption{82 bodies at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the
  fixed-pressure-drop condition. The color is the vorticity of fluid. In
  this simulation, we use $N_\iin = 256$ discretization points on the
  body, $N_\out = 1024$ points on the outer wall, a time-step of
  $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and
  $\sigma=10/256$.}
\end{figure}

{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow. The background
flow is 
\begin{align}
  \UU(\xx)=U \left[
  \begin{array}{c}
    1-y^2 \\ 0
  \end{array}
  \right]
\end{align}
with floating flow rate $U$ such that pressure drop is fixed from x = -2 to x = 2.
We record the vorticity of 
fluid during the bodies erosion in Fig.~\ref{fig:Eroding100vort} and 
measure the gap sizes between bodies in Fig.~\ref{fig:Eroding100gap} at four time steps.

\begin{figure}[H]
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_50}
\caption{100 bodies with 318 gaps at t= 0.005}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_100}
\caption{99 bodies with 312 gaps at t= 0.01}
\end{subfigure}
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_150}
\caption{94 bodies with 294 gaps at t= 0.015}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics*[width =\linewidth]{./figs/gap_hist100_200}
\caption{82 bodies with 254 gaps at t= 0.02}
\end{subfigure}
\caption{\label{fig:Eroding100gap} The histograms of gaps in the case of erosion of 100 bodies at four time steps.}
\end{figure}

@@

In Fig.~\ref{fig:Eroding100tort}(b) we record the 
local tortuosity $\tau(y)$ for $y$ on the starting cross section x = -1.
It is a discontinous function and the maximum of $\tau$ in the case of 100 bodies is
is 1.2547 and the minimum is 1.0003. This function $\tau$
has more jumps than the one in the case of 20 bodies but its maximum 
is smaller than the maximum in the case of 20 bodies. 
The jump in this graph means the neighboring trajectories are splitted by bodies
so it is reasonable to have more jumps in the case of 100-body than the case of 20-body
since there are more bodies in the former case. To understand the meaning of jump 
of $\tau$, we use the data we got from local tortuosity $\tau(y)$
to find the difference of $\tau$ at the neighboring tracers in Fig.~\ref{fig:Eroding100tort}(c) 
and draw 50 pairs of neighboring trajectories which have the largest difference of $\tau$
in Fig.~\ref{fig:Eroding100tort_traj}. These pairs of two neighboring trajectories are splitted by bodies
then rejoin with each other and it causes the difference of $\tau$ with respect to the neighboring trajectories.   
We also can get the idea why the maximum value of $\tau$ is smaller 
than the one in the case of 20 bodies . 
The most of the bodies in this case are smaller than those in the case of 20 bodies.
So when two neighboring trajectories are splitted on the left side by a smaller body they do not
travel as far as the two splitted by a bigger body do after they rejoin on the right side. 
}

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The historical trajectories of 
200 tracers released at x = -1 in the fluid with multiple bodies.}
\end{center}
\end{figure}
